\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-26 doc/paper.tex
Fixes #170.

	\subsection{Education} When Robillard and Deline researched common obstacles
	for programmers learning new APIs, they concluded that one of the most
	important elements of a good API was the use of code examples to demonstrate
	function use. Examples in APIs, furthermore, come in a variety of forms: small
	snippets or tutorials that show only the intended function, sample applications
	that incorporate the function in a broader context, or even production code
	that employs the function but was not initially intended to be an illustrative
	example~\cite{robillard2011field}. Of these categories, \toolname aligns
	entirely with the last; when a user chooses to explore a particular function
	node, they will see examples of that formula as it was used in a working
	environment, with the specifics depending on the dataset the tool is using.
	\par

	Furthermore, Robillard and Deline's study makes the case for examples that show
	``API usage patterns involving more than one method call"
	\cite{robillard2011field}. Examples that show only a single function, they
	find, are too simple, whereas those demonstrating the interaction of functions
	will equip users for more complex tasks. \toolname is especially suited for
	this focus on combination; consider again the question in the walkthrough
	(Section \ref{sec:walkthrough}), asking which functions and operations are used
	as conditions in IF. The design of this tool emphasizes the connection, then,
	between what functions like ISNA and AND return and what IF accepts, and
	specific examples for any of these combinations are only a click away.

>>>>

	\subsection{Education} When Robillard and Deline researched common obstacles
	for programmers learning new APIs, they concluded that one of the most
	important elements of a good API was the use of code examples to demonstrate
	function use~\cite{robillard2011field}. Examples in APIs, furthermore, come in a variety of forms: small
	snippets or tutorials that show only the intended function, sample applications
	that incorporate the function in a broader context, or even production code
	that employs the function but was not initially intended to be an illustrative
	example. Of these categories, \toolname aligns
	entirely with the last; when a user chooses to explore a particular function
	node, they will see examples of that formula as it was used in a working
	environment, with the specifics depending on the dataset the tool is using.
	\par

	Furthermore, Robillard and Deline's study makes the case for examples that show
	``API usage patterns involving more than one method call"~\cite{robillard2011field}. Examples that show only a single function, they
	find, are too simple, whereas those demonstrating the interaction of functions
	will equip users for more complex tasks. \toolname is especially suited for
	this focus on combination; consider again the question in the walkthrough
	(Section \ref{sec:walkthrough}), asking which functions and operations are used
	as conditions in IF. The design of this tool emphasizes the connection, then,
	between what functions like ISNA and AND return and what IF accepts, and
	specific examples for any of these combinations are only a click away.
